Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Wording, and a comment for @kazu

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock provides markup syntax for code blocks, indicated with ({\tt
>}).
For example, the {\tt containers} packages contains a Haddock comment
with the following code block.

>>>>

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.

\begin{quote}
    sol: @kazu should we cite package documentation, to support this?
    I'm aware of:
    \begin{itemize}
        \item filepath
        \item containers
    \end{itemize}
\end{quote}

Here is an example from the {\tt containers} packages.
